--- 
title: "Report on RStudio"
author: "Ian Davis"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Technical Report on RStudio"
---

From: [address]

To: [address]

# Letter of Transmission

Dear Dr. Kares,

This report is a profile of the company RStudio. It focusses on how RStudio affected the evolution of data analytics by its creation and support of tools that modernize the R programming language and statistical computing environment. RStudio also produces materials that teach these tools, including blogs, interactive tutorials, and books.

I hope this report meets your expectations

Respectfully,


Ian Davis



```{r eval=FALSE, warning=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
